\documentclass[11pt]{article}
\usepackage[a4paper, margin=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5} 

% Formatting for section titles
\titleformat{\section}{\bfseries\Large}{}{0em}{}
\titleformat{\subsection}{\bfseries}{}{0em}{}

% Name and contact information
\begin{document}
\begin{center}
    {\LARGE \textbf{Jonathan Z. Ong (He/Him)}} \\[0.5em]
    \faEnvelope \hspace{0.05cm} \href{mailto:jonathanzong98@gmail.com}{jonathanzong98@gmail.com} \hspace{0.2cm} 
    \faPhone \hspace{0.05cm} +65 8654 6278 \hspace{0.2cm} 
    \faGlobe \hspace{0.05cm} \url{https://jonathanongzm.github.io/}
\end{center}

\section*{EDUCATION}
\hrule
\textbf{Nanyang Technological University} \hfill Singapore \\
MA in Psychology, GPA: 5.00/5.00 \hfill Jan 2023--Jan 2025\\ 
Advisors: Professors Victoria Leong and George Augustine\\
\textit{Project: Sociometric AI Screening Tool to Risk-Stratify Infant Neurodevelopmental Trajectories}
\begin{itemize}[leftmargin=1.2cm]
    \item Collected, preprocessed, and analyzed multimodal time-series data, including EEG, ECG, and behavioral data from parent-child dyads using MATLAB, R, and Python.
    \item Designed and optimized naturalistic tasks to assess executive functions and neurodevelopmental trajectories in children aged 6–36 months, in a parent-child social interactive context.
    \item Developed analytical pipelines to generate rich behavioral data from well-designed ethograms, perform data wrangling to synchronize multimodal data streams, and compute novel metrics as precursors of executive functions.

\end{itemize}
\textit{Project: Optogenetic Parent-Offspring Mouse Model of Neural Synchrony and Social Learning}
\begin{itemize}[leftmargin=1.2cm]
    \item Modified the social transmission of food preference paradigm for parent-child dyads, compatible with optogenetics and behavioral recording, to investigate the neurobehavioral mechanisms of social learning.
    \item Managed mouse husbandry, including breeding, genotyping, and maintenance of transgenic lines, with strict adherence to animal welfare and ethical standards.
    \item Performed brain harvests and immunohistochemistry to verify optogenetic manipulation in the medial prefrontal cortex.
    \item Thesis: Desynchronized Interbrain Neural Activity in the Medial Prefrontal Cortex Disrupts Behavior Contingencies and Mouse Parent-to-Child Transmission of Food Safety.
\end{itemize}

\textbf{Monash University} \hfill Malaysia \\
BPsych(Hons), GPA: 4.00/4.00, Best Graduate Award \hfill Mar 2021--Dec 2021\\
\textit{Thesis: The Relationship between Romantic Dispositions and Romantic Need Prioritization in Single Adult Malaysians: The Moderating Role of Gender}

\textbf{Monash University} \hfill Malaysia \\
BPsych, GPA: 3.92/4.00, Best Graduate Award \hfill Jul 2017--Jul 2020

\section*{HONORS \& AWARDS}
\hrule
\textbf{A*STAR Fully-Sponsored Master's Studentship} \hfill Jan 2023--Jan 2025\\ 
Nanyang Technological University (PI: Professor Victoria Leong)

\textbf{Two-Time Best Graduate Award Recipient} \hfill 2020, 2021\\ 
BPsych and BPsych(Hons), Monash University Malaysia

\textbf{Graduate Pathway Research Scholarship (\textasciitilde{}USD 2,400)}\hfill 2021\\ 
BPsych(Hons), Monash University Malaysia

\textbf{Undergraduate Studies Loan Exemption (\textasciitilde{}USD 6,200)} \hfill 2021\\ 
BPsych, Malaysian National Higher Education Fund Corporation

\textbf{Monash High Achiever Award} \hfill 2019\\ 
BPsych, Monash University Malaysia

\section*{RESEARCH EXPERIENCE}
\hrule
\textbf{Nanyang Technological University} \hfill Singapore \\
Graduate Research Assistant; PI: Prof Victoria Leong \hfill Jan 2024--Present \\
\textit{Project: Assessing Social Influences on Executive Function in Infants}
\begin{itemize}[leftmargin=1.2cm]
    \item Coordinating an interdisciplinary team of psychologists, neuroscientists, engineers, and AI/data scientists to develop novel social interaction metrics for clinical and commercial applications.
\end{itemize}

\textbf{Sunway University} \hfill Malaysia \\
Research Assistant; PI: Professor Alexandre Schaefer \hfill Jul 2022--Nov 2022\\
\textit{Project: Aging, Health and Well-Being (AGEWELL)}
\begin{itemize}[leftmargin=1.2cm]
    \item Conducted community outreach to recruit a socioeconomically diverse Malaysian cohort aged 60 and above and administered neuropsychological assessments to evaluate executive functions alongside EEG data acquisition.
    \item Preprocessed EEG data and computed event-related potentials as markers of cognitive aging in MATLAB.
    \item Performed general linear modeling in R to investigate the protective role of cognitive reserve against cognitive decline in older adults.
\end{itemize}

\textbf{Monash University} \hfill Malaysia \\
Research Assistant \hfill 2018--2022
\begin{itemize}[leftmargin=1.2cm]
    \item Conducted literature reviews and applied qualitative methods including transcription, Malay to English translation, and thematic coding to investigate cultural differences in cancer stigma (PI: Professor Elizabeth Jones).
    \item Collected and analyzed dyadic social interaction data from questionnaires and behavior coding to examine individual differences in social perceptions using the Actor-Partner Interdependence Model (PI: Dr. Goh Pei Hwa).
    \item Co-organized the first and second Southeast Asian Indigenous Psychology Scientific Meeting, 2021 and 2022, marking the inaugural gathering of Southeast Asian Indigenous Psychology scholars (Supervisor: Dr. Rachel Sing-Kiat Ting).
\end{itemize}

\section*{PEER-REVIEWED PUBLICATIONS}
\hrule
Goh, P. H., \& \textbf{Ong, J. Z.\textsuperscript{*}} (2022). It's a guy thing: Sex as a moderator of the relationship between social anxiety and perception of interpersonal warmth in initial heterosexual interactions. \textit{Asian Journal of Social Psychology}, 25(4), 806–815. \href{https://doi.org/10.1111/ajsp.12536}{https://doi.org/10.1111/ajsp.12536}

Ham, G. X., \textbf{Ong, J. Z.}, Augustine, G. J., \& Leong, V. (2024). Protocol to study dam-pup social transmission using a modified paradigm for transmission of food preference. \textit{STAR Protocols}, 5(2), 103077. \href{https://doi.org/10.1016/j.xpro.2024.103077}{https://doi.org/10.1016/j.xpro.2024.103077}

\section*{IN PREPARATION}
\hrule
Koh, D. M., \textbf{Ong, J. Z.}, \& Goh, P. H. (Under review). Helicopter Parenting and Social Competence among Single Malaysian Adults: Filial Piety as a Moderator. \textit{Current Psychology}.

Vafa, S., \textbf{Ong, J. Z.}, Yong, M. H., Arokiaraj, A. S., Shee, D., Chia, Y. C., \& Schaefer, A. (Revised and resubmitted). Online cognitive testing with Asian older adults during the COVID-19 pandemic: A proof-of-feasibility study. Preprint: \href{https://doi.org/10.31234/osf.io/t8exs}{https://doi.org/10.31234/osf.io/t8exs}. \textit{BMC Psychology}.

Optogenetic synchronization of rodent dam-pup prefrontal cortex increases socially contingent behavior and stable states for knowledge transmission (in preparation).

Protocol for longitudinal imaging of parent–infant social interactive behavior and neurophysiology to assess emerging executive functions in infants with and without neurodevelopmental risks (in preparation).

\section*{CONFERENCE POSTERS \& MEDIA}
\hrule
Marzuki, A. A., Thanaraju, A., \textbf{Ong, J. Z.}, Yip, W. Z., Yap, Z. J., \dots Schaefer, A. (2022). AGEWELL: Investigating the predictors of healthy neurocognitive aging in a socioeconomically and ethnically diverse Malaysian cohort. Poster awarded People's Choice Award at the Annual Meeting of the Society for Neuroscience 2022, Singapore Chapter. \href{http://doi.org/10.13140/RG.2.2.18928.74241}{http://doi.org/10.13140/RG.2.2.18928.74241}

\textbf{Ong, J. Z.} \& Goh, P. H. (2020). It's a guy thing: Sex as a moderator of the relationship between social anxiety and perception of interpersonal warmth in initial heterosexual interactions. Poster awarded 3rd Place for Best Poster Presentation at the Jeffrey Cheah School of Medicine and Health Sciences Research Symposium (2020). \href{http://doi.org/10.13140/RG.2.2.12484.85121}{http://doi.org/10.13140/RG.2.2.12484.85121}

Leong, V., Campolo, D., \& \textbf{Ong, J. Z.} (2024). Understanding infants’ mental skills: New AI and sensor tools to measure development. \textit{Nanyang Technological University Magazine: Pushing Frontiers, (23),} 22–23. \href{https://jonathanongzm.github.io/assets/pdf/pushing_frontiers.pdf}{[PDF]}

\section*{TEACHING  \&  MENTORING}
\hrule
\textbf{Nanyang Technological University}\hfill Singapore 
\begin{itemize}[leftmargin=1.2cm]
    \item Teaching Assistant and Grader for Introductory Psychology (Fall 2023).
    \item Mentor for two Thesis students and three Undergraduate RAs (2023–Present).
\end{itemize}

\textbf{Monash University}\hfill Malaysia 
\begin{itemize}[leftmargin=1.2cm]
    \item Grader for Biological Psychology, Developmental Psychology, Contemporary Social Psychology, and Research Theory and Methods (2022).
    \item Peer Tutor for Introductory Psychology (Spring 2022), Research Methods and Theory (Fall 2021, 2022).
    \item Volunteer English Teacher for a class of 15 Chin refugee children (Fall 2017).
\end{itemize}

\textbf{SK \& SMK Bandar Tun Hussein Onn 2}\hfill Malaysia 
\begin{itemize}[leftmargin=1.2cm]
    \item Part-Time Teacher for elementary (Jun–Dec 2016) and high school (Feb–May 2017) students, with class sizes of about 30.
\end{itemize}

\section*{SKILLS}
\hrule
\textbf{Experimental Methods} \\
EEG and ECG Hyperscanning, Naturalistic Behavioral Recordings, Parent-Infant Interactions, Task Design and Development for Human and Rodent Models.

\textbf{Computational Skills} \\
Proficient in R, MATLAB, Python, SPSS, JASP, and Statistica, with experience in Generalized Linear Modeling, Structural Equation Modeling, Dynamical Systems Modeling, Time Series Analysis, Data Wrangling, Data Visualization, Analytical Pipeline Development, and Matrix Operations.

\textbf{Typesetting and Web Development} \\
Experienced in \LaTeX{} for document typesetting, and HTML, CSS, and Ruby for website development.

\textbf{Wet Lab Skills} \\
Mouse Husbandry, Genotyping, Brain Harvest, Immunohistochemistry, Optogenetics.

\end{document}
